\chapter{Supporting Tables and Reproducibility}
\label{ch:appendix}
\raggedbottom

\section{Regression Diagnostics}

This appendix reports only supporting material that is useful for checking the main analysis without repeating the figures already discussed in the thesis chapters. Table~\ref{tab:appendix_full_pooled_regression} gives the full pooled baseline regression, including the year indicators omitted from the compact main table. The omitted year is 2015.

\begin{table}[H]
\centering
\scriptsize
\caption{Full pooled baseline regression with year indicators}
\label{tab:appendix_full_pooled_regression}
\input{tables/appendix_full_pooled_regression}
\end{table}

Table~\ref{tab:appendix_regression_vif_diagnostics} reports variance inflation factors for the baseline covariates. The diagnostics are included to document the degree of collinearity among the main regressors used in the complete-case model.

\begin{table}[H]
\centering
\small
\caption{Variance inflation factors for baseline covariates}
\label{tab:appendix_regression_vif_diagnostics}
\input{tables/regression_vif_diagnostics}
\end{table}

\section{Data Sources and Reproducibility}

Table~\ref{tab:appendix_eurostat_sources} lists the Eurostat tables and filters used to construct the datasets. The primary outcome is hlth\_silc\_08, while hlth\_silc\_08b is used only as the robustness outcome because its denominator differs from the main population-level indicator.

\begin{table}[H]
\centering
\scriptsize
\caption{Eurostat source tables, filters, and extraction dates}
\label{tab:appendix_eurostat_sources}
\input{tables/eurostat_sources_appendix}
\end{table}

Table~\ref{tab:appendix_software_versions} records the main software environment used for data processing, modelling, and figure generation.

\begin{table}[H]
\centering
\small
\caption{Python and library versions}
\label{tab:appendix_software_versions}
\input{tables/software_versions}
\end{table}

Table~\ref{tab:processed_data_dictionary_summary} summarises the processed data files submitted with the thesis package. The full column-level data dictionary is written to \texttt{outputs/processed\_data\_dictionary.csv}.

\input{tables/processed_data_dictionary_summary}

Table~\ref{tab:output_generation_map} gives a compact map from thesis output groups to the scripts that generate them. Full file-level paths and exact source filenames are written to \texttt{outputs/table\_figure\_generation\_map.csv}.

\begin{table}[H]
\centering
\scriptsize
\caption{Table and figure generation map}
\label{tab:output_generation_map}
\begin{tabularx}{\textwidth}{@{}p{0.32\textwidth}p{0.22\textwidth}Y@{}}
\toprule
Output group & Script group & Main inputs \\
\midrule
Panel construction, descriptive outputs, baseline regressions, source register & Full analysis & Eurostat raw downloads and processed country-year panel \\
Conceptual selection and estimand diagram & Diagram generation & Author-defined conceptual roles documented in Chapter~\ref{ch:background_literature} \\
Missingness, IPW, MI, MNAR, and robustness diagnostics & Missingness robustness & Processed panel and imputed panel draws \\
Multi-outcome registry, monitoring benchmark, drift diagnostics, and coefficient matrix & Multi-outcome builders & Multi-outcome Eurostat extracts and processed panel \\
Semi-synthetic missingness simulation & Simulation & Reference panel and simulation configuration \\
Prediction benchmark and supporting descriptive checks & Appendix analyses & Prediction panel, citizenship extract, and \texttt{hlth\_silc\_08b} overlap panel \\
Manifest, software versions, hashes, and output checks & Master summary & Generated tables, figures, outputs, and scripts \\
\bottomrule
\end{tabularx}
\end{table}

The computational workflow is fully scripted in the local project directory. Raw Eurostat JSON downloads are stored in \texttt{data/raw}; processed country-year files are stored in \texttt{data/processed}; generated CSV diagnostics are stored in \texttt{outputs}; generated LaTeX tables are stored in \texttt{tables}; and generated figures are stored in \texttt{figures}. The reproduction command sequence is:
\begin{lstlisting}[basicstyle=\ttfamily\footnotesize,breaklines=true,columns=fullflexible]
python src/run_full_thesis_analysis.py
python src/generate_conceptual_selection_diagram.py
python src/run_missingness_robustness.py
python src/build_multi_outcome_indicator_registry.py
python src/build_multi_outcome_monitoring_benchmark.py
python src/build_multi_outcome_drift_diagnostics.py
python src/build_outcome_estimand_stability_matrix.py
python src/run_missingness_simulation.py --replicates 100 --imputations 2 --seed 42
python src/build_reporting_protocol_tables.py
python src/run_step5_ml_analysis.py
python src/run_step6_additional_analysis.py
python src/run_step7_master_summary.py
\end{lstlisting}
The raw-data download workflow is part of the first command: it calls the Eurostat API for the main outcome, robustness outcome, citizenship table, population weights, and control/feature covariates using the filters listed in Table~\ref{tab:appendix_eurostat_sources}. The main table and figure generation map is:
\begin{itemize}
    \item the full-analysis script builds the panel, descriptive figures, baseline regressions, population-weighted trends, and source register;
    \item the diagram script creates the conceptual selection and estimand figure;
    \item the missingness script creates target-population sensitivity, IPW, MI, and poverty-robustness outputs;
    \item the prediction script creates one-year-ahead baselines, benchmark-model comparisons, and country-holdout validation;
    \item the additional-analysis script creates citizenship paired-gap checks and \texttt{hlth\_silc\_08b} denominator robustness;
    \item the summary script creates the manifest, software versions, command order, hashes, and output checks.
\end{itemize}
All stochastic analyses use random seed 42 unless explicitly stated otherwise. The reproducibility manifest records Python and package versions, input and script hashes, output hashes, command order, the population-weighting source, and the prediction hyperparameter grids. The submitted package also includes raw-download instructions, an output hash manifest, and a reproducibility archive under \texttt{outputs}. The thesis does not cite a public code repository unless a validated public archive is created; reproducibility is documented through the submitted local scripts, raw downloads, processed files, generated outputs, source register, and manifest.
