\chapter{Introduction}
\label{ch:introduction}

\section{Motivation}

Public unmet-care indicators are widely used to compare access barriers across European health systems. Eurostat EU-SILC indicators are especially useful because they provide repeated, public, country-year measures of self-reported unmet medical and dental care need. These indicators can describe cost barriers, distance barriers, waiting-list barriers, and differences between population-denominator and need-denominator definitions.

The same public data can also mislead if the analytical target is left implicit. Aggregate panels do not contain one natural population. The population changes when the analyst changes the denominator, country universe, weighting rule, time window, row-selection rule, or missing-data assumption. A regression that requires every covariate can quietly move the analysis from a broad monitoring panel to a selected covariate-complete subset. This movement is the central problem studied in the thesis.

\section{Target-Population Drift}

The thesis uses the term \emph{target-population drift} for the movement from an intended monitoring target to a different analytical target created by denominator choice, country-universe restriction, population weighting, covariate completeness, or missing-data modelling. In this setting, the same poverty/social-exclusion coefficient can refer to different objects: an equal-country complete-case panel, a population-weighted resident panel, an EU-27 subset, an IPW-reweighted selected panel, or a model-imputed outcome-observed target.

The country universe is defined before model interpretation. The full Eurostat-available universe means national units observed in the selected Eurostat tables after excluding EU and euro-area aggregates. EU-27 sensitivity is mandatory because the substantive phrase ``European'' is otherwise too broad for public aggregate data. Smaller country groups are reported only when coverage is stable enough to be interpretable.

\section{Research Questions}

The thesis is organized around five research questions:

\begin{description}
    \item[RQ1: Indicator dependence.] How do unmet-care monitoring conclusions change across medical versus dental care, population-denominator versus need-denominator indicators, and barrier-specific definitions such as cost, distance, and waiting lists?
    \item[RQ2: Target-population drift.] How much does complete-case covariate selection change the country-year population used for regression, and which variables, countries, years, and country groups drive this attrition?
    \item[RQ3: Coefficient stability.] Are social-vulnerability coefficients stable across complete-case, population-weighted, balanced-outcome, IPW, MAR-imputed, and MNAR-shifted estimands?
    \item[RQ4: Simulation validity.] Under semi-synthetic Eurostat-style missingness, when does complete-case fixed-effects estimation recover the reference estimand, and when does it produce bias, sign instability, interval undercoverage, or wrong substantive conclusions?
    \item[RQ5: Reporting protocol.] Can a reproducible target-population drift audit classify public aggregate-panel findings as stable, target-dependent, denominator-dependent, missingness-dependent, imputation-model-dependent, or non-identifiable?
\end{description}

Poverty or social exclusion remains the main stress-test covariate. It is theoretically relevant to affordability and social vulnerability, and the existing primary-outcome analysis shows that the observed outcome panel contains 608 country-years while the baseline complete-case fixed-effects model uses 282 rows. The thesis asks whether poverty-related aggregate interpretation is stable across explicitly defined estimands rather than treating any selected-panel estimate as the final answer.

\section{Audit Protocol}

An estimand is the country-year quantity targeted by a row set, denominator, weighting rule, country universe, and missing-data assumption. The audit protocol is a structured reporting procedure for documenting how these choices change the target population and interpretation of aggregate-panel estimates. It is not a new estimator and it does not make the aggregate data causal.

\begin{table}[htbp]
\centering
\scriptsize
\caption{Draft target-population drift audit checklist}
\label{tab:intro_audit_checklist}
\begin{tabular}{p{0.24\linewidth}p{0.66\linewidth}}
\toprule
Audit component & Required documentation \\
\midrule
Target definition & Unit, outcome denominator, country universe, time window, and weighting rule. \\
Coverage drift & Country-year coverage before and after each outcome, covariate, and population-weight requirement. \\
Selection distortion & Included-versus-excluded differences in outcome level, covariates, country groups, and time periods. \\
Estimand stability & Poverty/social-exclusion coefficient across complete-case, population-weighted, balanced, IPW, MAR-imputed, and MNAR-shifted targets. \\
Simulation validity & Behaviour of complete-case and missing-data estimators under semi-synthetic Eurostat-style missingness relative to a reference estimand. \\
Reporting classification & Final label explaining whether evidence is stable, target-dependent, denominator-dependent, missingness-dependent, imputation-model-dependent, or non-identifiable. \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:intro_audit_checklist} gives the draft checklist used to organize the thesis. The core estimands are outcome-observed monitoring targets, year-normalized population-weighted targets, complete-case fixed-effects targets, balanced-outcome targets, IPW diagnostic targets, MAR-imputed targets, and MNAR-shifted sensitivity targets. Population weighting changes the estimand; it is not automatically superior to equal-country monitoring. Multiple imputation is treated as sensitivity, not correction.

\begin{table}[htbp]
\centering
\scriptsize
\caption{Draft deterministic failure-mode labels}
\label{tab:intro_failure_modes}
\begin{tabular}{p{0.28\linewidth}p{0.62\linewidth}}
\toprule
Label & Interpretation \\
\midrule
Stable & Main estimand families give the same substantive direction and similar IQR-scale effects. \\
Target-dependent & Estimates change materially when the row set, balanced-outcome restriction, weighting rule, or country universe changes. \\
Denominator-dependent & Population-denominator and need-denominator indicators support different interpretations for the same care type or barrier. \\
Missingness-dependent & Complete-case, IPW, or imputed targets materially disagree after covariate missingness is addressed. \\
Imputation-model-dependent & MAR or MNAR imputation variants disagree strongly with each other. \\
Non-identifiable & Too few reliable estimand families are feasible, or available estimands conflict too strongly for a defensible coefficient interpretation. \\
\bottomrule
\end{tabular}
\end{table}

\section{Contributions}

The thesis makes five contributions.

\begin{enumerate}
    \item It formalizes target-population drift in public aggregate health-monitoring panels as movement across units, denominators, country universes, weighting rules, covariate-completeness rules, and missing-data assumptions.
    \item It builds a multi-outcome Eurostat benchmark for unmet medical and dental care indicators, including population-denominator and need-denominator outcomes where coverage is feasible.
    \item It applies a reproducible audit protocol to quantify outcome coverage, complete-case attrition, included/excluded imbalance, country/year retention, and coefficient stability across estimands.
    \item It uses semi-synthetic missingness simulations to evaluate when complete-case fixed-effects estimates recover a reference estimand and when they produce bias, sign instability, interval undercoverage, or wrong substantive conclusions.
    \item It provides reusable code, tests, data dictionaries, extraction records, output maps, and command sequences for reproducing the analysis.
\end{enumerate}

The contribution is methodological-applied. It improves how public aggregate health-access monitoring results are reported and interpreted without claiming individual-level mechanisms, policy effects, or a corrected poverty coefficient.

\section{Thesis Structure}

The upgraded thesis is organized around the audit protocol. Chapter 2 reviews healthcare access theory, Eurostat/EU-SILC measurement, ecological limits, target populations, missing data, and reporting discipline. Chapter 3 defines the public-data estimand registry. Chapter 4 presents the multi-outcome monitoring benchmark before modelling. Chapter 5 contains the empirical audit: target-population drift diagnostics, outcome-by-estimand coefficient stability, and the semi-synthetic missingness simulation. Chapter 6 presents the reporting protocol, final classification of findings, and conclusion. Prediction, citizenship, and long model ladders are treated as supporting appendix material rather than as independent thesis claims.
