\begingroup
\tiny
\begin{longtable}{@{}p{0.11\textwidth}p{0.39\textwidth}p{0.13\textwidth}p{0.11\textwidth}@{}}
\caption{Table and figure generation map}\label{tab:output_generation_map}\\
\toprule
Use & Output & Script & Input \\
\midrule
\endfirsthead
\toprule
Use & Output & Script & Input \\
\midrule
\endhead
App. & 08b\_minus\_08\_differen... & extra & C/08b \\
App. & 08b\_vs\_08\_scatter.pdf & extra & C/08b \\
App. & citizenship\_gap\_corre... & extra & C/08b \\
App. & citizenship\_unmet\_nee... & extra & C/08b \\
App. & citizenship\_unmet\_nee... & extra & C/08b \\
App. & citizenship\_unmet\_nee... & extra & C/08b \\
Ch. 4; Ch. 1; Ch. 5 & complete\_case\_attriti... & full & Panel \\
Ch. 2 & conceptual\_selection\_... & diagram & Concept \\
App. & conclusion\_stability\_... & stability & Panel \\
App. & convergence\_sigma.pdf & extra & C/08b \\
App. & descriptive\_country\_r... & full & Panel \\
App. & descriptive\_country\_r... & full & Panel \\
App. & descriptive\_country\_y... & full & Panel \\
Ch. 4 & descriptive\_estimand\_... & full & Panel \\
App. & descriptive\_eu\_trend.pdf & full & Panel \\
App. & descriptive\_trend\_eur... & full & Panel \\
App. & descriptive\_trend\_wit... & extra & C/08b \\
App. & drift\_stability\_map.pdf & stability & Panel \\
App. & leave\_one\_country\_out... & missing & Panel \\
App. & leave\_one\_year\_out\_po... & missing & Panel \\
Ch. 5 & mi\_coefficient\_distri... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
App. & mi\_imputed\_share\_heat... & missing & Panel \\
Ch. 5 & mi\_observed\_vs\_impute... & missing & Panel \\
App. & mi\_observed\_vs\_impute... & missing & Panel \\
App. & mi\_observed\_vs\_impute... & missing & Panel \\
App. & mi\_observed\_vs\_impute... & missing & Panel \\
App. & mi\_observed\_vs\_impute... & missing & Panel \\
App. & mi\_observed\_vs\_impute... & missing & Panel \\
App. & mi\_observed\_vs\_impute... & missing & Panel \\
App. & mi\_observed\_vs\_impute... & missing & Panel \\
App. & mi\_observed\_vs\_impute... & missing & Panel \\
Ch. 4 & missingness\_heatmap.pdf & full & Panel \\
App. & missingness\_heatmap\_c... & full & Panel \\
Ch. 4 & missingness\_heatmap\_f... & full & Panel \\
App. & missingness\_heatmap\_o... & full & Panel \\
App. & missingness\_heatmap\_p... & full & Panel \\
Ch. 4 & missingness\_heatmap\_s... & full & Panel \\
Ch. 5 & missingness\_inclusion... & full & Panel \\
App. & ml\_actual\_vs\_predicte... & ml & ML \\
App. & ml\_actual\_vs\_predicte... & ml & ML \\
App. & ml\_actual\_vs\_predicte... & ml & ML \\
App. & ml\_calibration\_plot.pdf & ml & ML \\
App. & ml\_expanding\_window\_v... & ml & ML \\
App. & ml\_importance\_compari... & ml & ML \\
App. & ml\_importance\_stabili... & ml & ML \\
App. & ml\_learning\_curves.pdf & ml & ML \\
App. & ml\_permutation\_vs\_imp... & ml & ML \\
App. & ml\_residuals\_by\_count... & ml & ML \\
App. & ml\_residuals\_by\_count... & ml & ML \\
App. & ml\_residuals\_by\_count... & ml & ML \\
App. & ml\_residuals\_vs\_predi... & ml & ML \\
App. & ml\_residuals\_vs\_predi... & ml & ML \\
App. & ml\_residuals\_vs\_predi... & ml & ML \\
App. & ml\_tree\_feature\_impor... & ml & ML \\
App. & ml\_validation\_tuning\_... & ml & ML \\
Ch. 5 & mnar\_tipping\_point\_cu... & missing & Panel \\
App. & model\_correlations\_he... & full & Panel \\
Ch. 5 & model\_ladder\_coeffici... & full & Panel \\
App.; Ch. 4 & multi\_outcome\_monitor... & benchmark & Panel \\
App. & multi\_outcome\_primary... & full & Panel \\
Ch. 5 & multi\_outcome\_retenti... & drift & Panel \\
Ch. 5 & outcome\_estimand\_coef... & matrix & Panel \\
App. & outcome\_missingness\_h... & full & Panel \\
App. & panel\_correlations\_he... & full & Panel \\
App. & panel\_heterogeneity.pdf & full & Panel \\
App. & panel\_variable\_distri... & full & Panel \\
Ch. 3 & population\_weighted\_t... & full & Panel \\
App. & poverty\_robustness\_fo... & missing & Panel \\
App. & regression\_fe\_coeffic... & missing & Panel \\
App. & regression\_robustness... & full & Panel \\
App. & scatter\_unmet\_vs\_comp... & full & Panel \\
App. & scatter\_unmet\_vs\_gdp\_... & full & Panel \\
App. & scatter\_unmet\_vs\_gini... & full & Panel \\
App. & scatter\_unmet\_vs\_gove... & full & Panel \\
App. & scatter\_unmet\_vs\_hosp... & full & Panel \\
App. & scatter\_unmet\_vs\_log\_... & full & Panel \\
App. & scatter\_unmet\_vs\_long... & full & Panel \\
App. & scatter\_unmet\_vs\_oop\_... & full & Panel \\
App. & scatter\_unmet\_vs\_phys... & full & Panel \\
App. & scatter\_unmet\_vs\_pove... & missing & Panel \\
App. & scatter\_unmet\_vs\_unem... & full & Panel \\
Ch. 5 & simulation\_bias\_by\_me... & sim & Panel \\
App. & simulation\_target\_dis... & sim & Panel \\
Ch. 5 & simulation\_tdi\_vs\_err... & sim & Panel \\
Ch. 5 & simulation\_wrong\_conc... & sim & Panel \\
App. & target\_drift\_componen... & stability & Panel \\
App. & tree\_feature\_importan... & full & Panel \\
App. & unmet\_need\_trends\_all... & full & Panel \\
App. & unmet\_need\_vs\_gdp\_per... & full & Panel \\
App. & unmet\_need\_vs\_poverty... & missing & Panel \\
App. & unmet\_need\_vs\_unemplo... & full & Panel \\
App. & appendix\_full\_pooled\_... & full & Panel \\
App. & attrition\_by\_country\_... & full & Panel \\
Ch. 4 & attrition\_by\_country\_... & full & Panel \\
Ch. 4 & attrition\_by\_covariat... & full & Panel \\
App. & attrition\_by\_year.tex & full & Panel \\
App. & citizenship\_gap\_clust... & extra & C/08b \\
App. & citizenship\_gap\_regre... & extra & C/08b \\
App. & citizenship\_gap\_table... & extra & C/08b \\
Ch. 4; Ch. 1; Ch. 5 & complete\_case\_attriti... & full & Panel \\
Ch. 5 & complete\_case\_selecti... & missing & Panel \\
App. & conclusion\_stability.tex & stability & Panel \\
App. & country\_coverage.tex & full & Panel \\
Ch. 3 & country\_universe.tex & missing & Panel \\
App. & descriptive\_statistic... & full & Panel \\
Ch. 5 & estimand\_framework.tex & missing & Panel \\
App. & eurostat\_sources\_appe... & summary & Gen. \\
Ch. 7 & failure\_modes\_public\_... & protocol & Panel \\
Ch. 5 & fe\_fit\_diagnostics.tex & missing & Panel \\
Ch. 5 & fe\_inference\_comparis... & missing & Panel \\
Ch. 7 & final\_classification\_... & protocol & Panel \\
App. & formal\_estimand\_compo... & stability & Panel \\
Ch. 4 & included\_vs\_excluded\_... & full & Panel \\
Ch. 4 & leave\_one\_variable\_ou... & missing & Panel \\
Ch. 5 & main\_sensitivity\_ladd... & missing & Panel \\
Ch. 5 & mi\_diagnostics\_summar... & missing & Panel \\
Ch. 5 & mi\_pmm\_donor\_diagnost... & missing & Panel \\
Ch. 5 & mi\_variant\_summary.tex & missing & Panel \\
Ch. 4 & missingness\_compariso... & full & Panel \\
Ch. 5 & missingness\_robustnes... & missing & Panel \\
Ch. 6 & ml\_country\_holdout\_su... & ml & ML \\
App. & ml\_hyperparameter\_gri... & ml & ML \\
Ch. 6 & ml\_model\_performance\_... & ml & ML \\
Ch. 6 & ml\_naive\_baselines.tex & ml & ML \\
App. & ml\_paired\_tree\_mae\_di... & ml & ML \\
App. & ml\_test\_mae\_bootstrap... & ml & ML \\
App. & ml\_time\_aware\_fold\_re... & ml & ML \\
Ch. 5 & mnar\_sensitivity\_resu... & missing & Panel \\
Ch. 5 & mnar\_tipping\_point\_re... & missing & Panel \\
Ch. 5 & model\_ladder\_results.tex & full & Panel \\
Ch. 5 & multi\_outcome\_attriti... & drift & Panel \\
App. & multi\_outcome\_country... & full & Panel \\
Ch. 4 & multi\_outcome\_coverag... & benchmark & Panel \\
Ch. 5 & multi\_outcome\_include... & drift & Panel \\
Ch. 4 & multi\_outcome\_monitor... & benchmark & Panel \\
App. & multi\_outcome\_primary... & full & Panel \\
App. & multiple\_imputation\_s... & full & Panel \\
Ch. 5 & outcome\_estimand\_coef... & matrix & Panel \\
App. & outcome\_failure\_class... & full & Panel \\
App. & output\_generation\_map... & summary & Gen. \\
App. & poverty\_robustness\_su... & missing & Panel \\
App. & processed\_data\_dictio... & summary & Gen. \\
Ch. 3; Ch. 4 & public\_data\_estimand\_... & registry & Panel \\
App. & reduced\_covariate\_sen... & full & Panel \\
App. & regression\_country\_gr... & full & Panel \\
App. & regression\_crisis\_exc... & full & Panel \\
App. & regression\_lag\_robust... & full & Panel \\
Ch. 5 & regression\_main\_resul... & full & Panel \\
App. & regression\_multilevel... & full & Panel \\
App. & regression\_robustness... & full & Panel \\
App. & regression\_sensitivit... & full & Panel \\
App. & regression\_sensitivit... & full & Panel \\
App. & regression\_vif.tex & full & Panel \\
App. & regression\_vif\_diagno... & full & Panel \\
Ch. 3 & robustness\_08b\_result... & extra & C/08b \\
App. & simulation\_complete\_c... & sim & Panel \\
Ch. 5 & simulation\_main\_summa... & sim & Panel \\
App. & simulation\_validation... & sim & Panel \\
App. & software\_versions.tex & summary & Gen. \\
App. & target\_drift\_componen... & stability & Panel \\
Ch. 7 & target\_population\_dri... & protocol & Panel \\
Ch. 5 & target\_population\_sen... & missing & Panel \\
Ch. 5 & universe\_sensitivity\_... & full & Panel \\
Ch. 3; Ch. 4; Ch. 5 & variable\_summary.tex & full & Panel \\
\bottomrule
\end{longtable}
\endgroup
